\section{Related Work}

Jaeger ~\cite{Jaeger} is an open-source distributed tracing project
that provides libraries for instrumenting distributed systems
in different languages as well as a frontend for viewing the traces
produced from these systems. Jaeger has vis idioms for visualizing
a single trace, for visualizing the dependencies between services
of the system, as well as an idiom for comparing 2 different traces.
However, it doesn't have any idiom for viewing an aggregate form of
multiple traces or for comparing groups of traces.

LightStep ~\cite{LightStep} is a start-up company that
creates solutions for real-time tracking of requests and metrics
in large-scale distributed systems. LightStep has vis idioms
for visualizing the structure of a single trace, for visualizing
the critical path of a single trace, and 
for visualizing various metrics collected for multiple traces.
Like Jaeger, LightStep also lacks a viz idiom for viewing aggregate
traces and for comparing groups of traces.

ShiViz ~\cite{ShiViz} is an interactive visualization tool
that visualizes communication graphs from distributed system execution
logs. As ShiViz is designed for visualizing logs and not individual traces,
ShiViz does not support comparisons of multiple traces.

The current state-of-the-art visualization tools for distributed tracing
have historically focused more on visualizing the structure and performance
characteristics of the traces using a waterfall idiom where
each process in the trace is modeled as a separate level in the waterfall.
However, these tools don't provide a idiom for finding
outlier traces and have very rudimentary visualizations for comparing
different traces which are tasks that target users actively wish to accomplish.
With TraViz, we address some of the shortcomings of existing tools
by providing a way for the users to compare the structure of two traces,
aggregate a group of traces, and integrate the traces with source code to provide more context
for debugging. We also provide an outlier exploration dashboard that allows
the users to filter along multiple dimensions of the dataset to quickly explore
the dataset and find possible outlier and erroneous traces.