\section{Results}

\subsection{Use Case 1: Outlier detection}

\subsection{Use Case 2: Source Code Optimization}

\subsection{Use Case 3: Service Dependency Analysis}

\subsection{Use Case 4: Finding differences in pair of traces}

\subsection{Use Case 5: Finding similarities in groups of traces}

\subsection{Use Case 6: Performance Analysis on a single trace}

\subsection{Informal User Study}

To evaluate the efficacy of TraViz, we conducted a very Informal user study
with 2 target users. One of the target users is one of the leading experts in distributed
tracing whereas the other user is an engineer at a large internet company where part of
their job is to analyze distributed traces. Due to geographical and time constraints,
the user study had to be done asynchronously where the target users were given
a deployed link of our tool and were asked to provide feedback regarding the user
experience.

Both of the target users liked the overview dashboard. Specifically, the leading expert
stated "Incorporating high-level metrics side-by-side with trace search and selection is a good idea and I like the dashboard you came 
up with". The source code view also garnered positive reviews as both the users thought
this is something that they would like to use with their data. The source code view
piqued the interest of the expert user as they thought it had the potential of getting
very deep as it was combining the static source code of the system with dynamic information
about actual executions. The other user thought the most useful visualization was the individual
trace view as it allowed them to view time spent by each thread individually.
The expert user thought that the dependency graph was useful but commented that
the graph should be directed as that is what users expect to see.

For the trace comparison and aggregation idioms, there was a general sense of confusion
across both the users. One of the users was particularly confused as to what each
of the nodes meant in the graph - whether the nodes were showing performance information
or structural differences or both. The expert user commented that the comparison and aggregation
graphs have some underlying ordering which wasn't being visualized. Although, they did acknowledge
that getting the ordering right for comparisons and aggregations is a hard task.

Given the feedback from the users, we believe that TraViz is partially successful in its endeavor of
being the most usable distributed tracing visual analysis tool.