\section{Related Work}

Jaeger ~\cite{Jaeger} is an open-source distributed tracing project
that provides libraries for instrumenting distributed systems
in different languages as well as a frontend for viewing the traces
produced from these systems. Jaeger has vis idioms for visualizing
a single trace, for visualizing the dependencies between services
of the system, as well as an idiom for comparing 2 different traces.
However, it doesn't have any idiom for viewing an aggregate form of
multiple traces or for comparing groups of traces.

LightStep ~\cite{LightStep} is a start-up company that
creates solutions for real-time tracking of requests and metrics
in large-scale distributed systems. LightStep has vis idioms
for visualizing the structure of a single trace, for visualizing
the critical path of a single trace, and 
for visualizing various metrics collected for multiple traces.
Like Jaeger, LightStep also lacks a viz idiom for viewing aggregate
traces and for comparing groups of traces.

ShiViz ~\cite{ShiViz} is an interactive visualization tool
that visualizes communication graphs from distributed system execution
logs. As ShiViz is designed for visualizing logs and not individual traces,
ShiViz does not support comparisons of multiple traces.

With TraViz, we want to address some of the shortcomings of existing tools
by providing a way for the users to compare the structure of a group of traces
as well as integrate the traces with source code to provide more context
for debugging.